---
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

# WWEAnalytics

## Overview

**WWEAnalytics** is an R package developed to analyze WWE Championship reign data.
It provides users with historical insights into WWE Championship reigns, including the duration of title reigns and comparative analysis across different eras and wrestlers.
The package includes easy-to-use functions for exploring reign patterns, interactive data visualizations with ggplot2, and a user-friendly Shiny app for interactive analysis.

## Key Features

-   **WWE Championship Reign Data**: Access comprehensive WWE Championship reign data, including duration, era classification, and gender breakdowns.

-   **Era-Based Analysis**: Explore title reign patterns across different WWE eras (Pre-1980s, 1980s-1990s, and 2000s-present) to understand how booking strategies have evolved.

-   **Interactive Visualization**: Use the Shiny app to visualize and interact with the data, including filtering by gender, era, and top wrestlers by reign length.

-   **Analysis Tools**: Built-in functions for calculating average reign lengths, comparing reigns across eras and gender, and visualizing trends in reign durations.

## Installation

Install the WWEAnalytics package directly from GitHub:

```{r}
# Install WWEAnalytics from GitHub
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-vsri0012")

```

## Usage

### 1. Launching the Shiny App

Run the Shiny app to interactively explore WWE Championship reign data:

```{r eval=FALSE}
WWEAnalytics::launch_shiny_app()
```

### 2. Analyzing Championship Reign Lengths with ggplot2

You can use ggplot2 with WWEAnalytics functions to visualize reign lengths across different eras and genders.

```{r eval=FALSE}
# Example: Comparing Average Reign Length by Era
library(dplyr)
library(ggplot2)

# Calculate average reign by era
average_reign <- average_reign_length_by_era(wrestling_data_clean)

# Plot the data
ggplot(average_reign, aes(x = era, y = avg_reign_length, fill = era)) +
  geom_col() +
  labs(title = "Average WWE Championship Reign Length by Era",
       x = "Era",
       y = "Average Reign Length (days)") +
  theme_minimal()

```

## Data Sources

-   **WWE Championship Reign Data**: Historical WWE Championship data containing reign details and wrestler demographics.

-   **Era Classification**: Categorized into Pre-1980, 1980s-1990s, and 2000s-present.

## License

This project is licensed under the MIT License.
See the LICENSE file for details.

## Contributions

Contributions are welcome!
Feel free to fork the repository, submit pull requests, or report issues to help improve the package.

## Documentation

For full documentation and tutorials, visit the pkgdown site here: [WWEAnalytics Documentation](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-vsri0012/)
