---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WWEAnalytics

<!-- badges: start -->
<!-- badges: end -->

## Purpose

WWEAnalytics is an R package designed to provide tools for exploring and analyzing WWE Championship reigns data. The package allows users to investigate average reign lengths, identify top wrestlers, and examine historical trends in professional wrestling. It includes both functions for statistical analysis and an interactive Shiny app for a more dynamic exploration of the data.

## Example Usage

Here’s a simple example demonstrating how to use the package:

```{r}
# Install the package (see instructions below)
remotes::install_github("vsri0012/WWEAnalytics")

# Load the WWEAnalytics package
library(WWEAnalytics)
```

## Installation

You can install the development version of WWEAnalytics like so:

```{r}
# Install from GitHub using remotes
remotes::install_github("vsri0012/WWEAnalytics")
```

Once installed, load the package with:

```{r}
library(WWEAnalytics)
library(tidyverse)
```

# Analyzing WWE Championship Reigns

Here’s how you can use some of the basic functions of the package to analyze the data:

```{r}
# Load the WWE Championship data
data("wrestling_data")

# Summary statistics of the reign lengths
summary(wrestling_data$days)
```

You can also include visualizations directly within your README using embedded R code chunks.

```{r}
# Create a plot of average reign lengths over time
library(ggplot2)
ggplot(wrestling_data, aes(x = year, y = days)) +
  geom_point() +
  geom_smooth(method = "loess") +
  labs(title = "Average WWE Championship Reign Length Over Time",
       x = "Year", y = "Reign Length (days)")
```

## Getting Help

If you encounter any issues or have questions about the WWEAnalytics package, you can:

- Refer to the package documentation by running:

```{r}
?WWEAnalytics
```

```{r}
help(package = "WWEAnalytics")
```

- Submit issues or feature requests on the GitHub Issues page.

- Contact the package author via email at vsri0012@student.monash.edu.



